---
title: "PEW income / job loss and psychological distress analysis"
author: "Grace Ringlein"
date: "2023-11-1"
output:
  html_document: 
    code_folding: hide
cache: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE)
```

# Load libraries

```{r libs, warning=FALSE,message=FALSE}
library(gtsummary)
library(foreign)
library(marginaleffects)
library(survey)
library(haven)
library(ggplot2)
library(cobalt)
library(WeightIt)
library(tidyverse)
library(here)
library(EValue)
```

## Read in data 

```{r}
# pewMH_dataset_merged_comp.sav geneerated by import_rawdata.Rmd  & make_composite_columns.Rmd 
W_wide <- read.spss(here("data","pewMH_dataset_merged_comp.sav"),to.data.frame = TRUE)

# directory in which to save figures
fig_path <- here("figures") 
```

## Measures 

### Demographics

```{r}
demographics <- 
  c("F_SEX_W64", # Sex (male or female)
    "F_AGECAT_W64", # Age (categorical)
    "F_RACETHN_W64", # Race and ethnicity (categorical)
    "F_MARITALMOD_W64", # Marital status (mod. combining divorced and separated)
    "F_EDUCCAT2_W64", # Education level
    "F_PARENT_W54", # Parent of a child under 18
    "F_CITIZEN_W64", # U.S. Citizen (yes/no)
    "F_CREGION_W64", # Census region (categorical)
    "F_METRO_W64" # Indicator of living in a metropolitan area
    )
```

### Life time diagnosis of mental illness

```{r}
lt <- "COVID_MENTAL_W64" # Life time diagnosis of mental health condition
```

### Financial Covariates

```{r}
financial <-
  c("INC_TIER2_W54", # Income tier (lower, middle, upper)
    "WORRY2c_comp_W54", # Financial strain (indicator, worries about bills every day/almost every day )
    "F_E3_W54", # Employment (Full-time, part-time, unemployed)
    "FINANCEa_W54", # Has savings account?
    "DEBT_SECURE_W54", # Has secure debt (composite indicator)
    "DEBT_INSECURE_W54") # Has unsecure debt (composite indicator) 
```

### Income or job loss variable
```{r}
exp <- "COVIDWORK_comp_bin_W72" # self or household job or income loss (composite indicator, see make_composite_columns.Rmd for details)
```

### Psychological distress 

```{r}
distress <- c("MH_TRACK_int_W64","MH_TRACK_int_W83","MH_TRACK_int_W114") 
pre_exp <- "MH_TRACK_int_W64" #pre-exposure distress
```

### Model covariates
```{r}
propensity_vars<- c(lt,demographics,financial,pre_exp)
```

### Labels for covariates (for tables and love plot)

```{r}
propensity_vars_labels <-list(
      MH_TRACK_int_W64 = "Psychological Distress (March 2020)",
      INC_TIER2_W54 = "Income Tier (Pre-pandemic)",
      WORRY2c_comp_W54="Financial Strain (Pre-pandemic)",
      COVID_MENTAL_W64="Lifetime Diagnosis of a Mental Health Condition",
      DEBT_SECURE_W54="Secure Debt (Pre-pandemic)",
      DEBT_INSECURE_W54="Unsecured Debt (Pre-pandemic)",
      FINANCEa_W54="Savings Account (Pre-pandemic)",
      F_E3_W54="Employment Status (Pre-pandemic)",
      F_AGECAT_W64="Age Category",
      F_MARITALMOD_W64="Marital Status",
      F_SEX_W64="Sex",
      F_EDUCCAT2_W64="Education Category",
      F_RACETHN_W64="Race and Ethnicity",
      F_PARENT_W54="Parent of a child under 18",
      F_CITIZEN_W64="Citizenship",
      F_CREGION_W64="Census Region",
      F_METRO_W64="Metropolitan Area","group"="group")

outcome_labels <- list(MH_TRACK_int_W64 = "Psychological distress in March 2020",
                       MH_TRACK_int_W83 = "Psychological distress in February 2021",
                       MH_TRACK_int_W114 = "Psychological distress in September 2022")

love_labels=c("MH_TRACK_int_W64" = "Mar. 2020 Psychological Distress",
         "F_CREGION_W64_Midwest"="Census Region: Midwest",
         "F_RACETHN_W64_Black non-Hispanic"="Race & Ethnicity: Black (Non-Hispanic)",
         "F_AGECAT_W64_50-64" = "Age: 50-64",
         "F_EDUCCAT2_W64_High school graduate"="Education: High school grad.",
         "F_SEX_W64_Female" ="Sex: Female",
         "F_EDUCCAT2_W64_Associate's degree" = "Education: Associate's",
         "F_MARITALMOD_W64_Divorced or Separated"= "Marital Status: Divorced/Separated",
         "INC_TIER2_W54_Lower income" = "Income Tier: Lower",
         "INC_TIER2_W54_Middle income"  ="Income Tier: Middle",
         "INC_TIER2_W54_Upper income"  ="Income Tier: Upper",
         "F_AGECAT_W64_30-49"= "Age: 30-49",
         "F_PARENT_W54_Yes"="Parent of child <18: Yes",
         "F_EDUCCAT2_W64_Less than high school" ="Education: < High School Graduate",
         "F_EDUCCAT2_W54_College graduate/some post grad"  ="Education: College Graduate",
         "F_CREGION_W64_West"="Census Region: West",
         "F_RACETHN_W64_Other"="Race & Ethnicity: Other",
         "INC_SDT1_W54_$80,000 to less than $90,000"="Income: $80-90k",
         "F_E3_W54_Full-time" ="Employment: Full-time",
         "COVID_MENTAL_W64_Yes" = "Lifetime Diagnosis of Mental Health Condition: Yes",
         "INC_SDT1_W54_$90,000 to less than $100,000" = "Income: $90-100k",
         "F_MARITALMOD_W64_Never been married"  = "Marital Status: Never married",
         "F_MARITALMOD_W64_Living with a partner" = "Marital Status: Living w/ partner",
         "F_CREGION_W64_Northeast"="Census Region: Northeast",
         "F_METRO_W64_Non-metropolitan" ="Metropolitan Area: No",
         "F_MARITALMOD_W64_Married" = "Marital Status: Married",
         "INC_SDT1_W54_$40,000 to less than $50,000"="Income: $40-50k",
         "INC_SDT1_W54_Less than $30,000" ="Income: <$30k",
         "F_EDUCCAT2_W64_Some college" ="Education: Some college",
         "F_EDUCCAT2_W64_College graduate+" ="Education: College graduate",
         "F_MARITALMOD_W64_Widowed"  ="Marital Status: Widowed",
         "INC_SDT1_W54_$70,000 to less than $80,000" = "Income: $70-80k",
         "F_CREGION_W64_South"="Census Region: South",
         "F_CITIZEN_W64_No" ="US Citizen: No",
        "F_CITIZEN_W64_Yes" ="US Citizen: Yes",
         "F_EDUCCAT2_W64_Postgraduate"="Education: Postgrad",
         "F_RACETHN_W64_Hispanic" ="Race & ethnicity: Hispanic",
         "FINANCEa_W54_No"="Savings Account: No",
        "FINANCEa_W54_Yes"="Savings Account: Yes",
         "F_RACETHN_W64_White non-Hispanic" = "Race & Ethnicity: White (Non-hispanic)",
         "F_AGECAT_W64_18-29"   ="Age: 18-29",
         "F_E3_W54_Part-time"="Employment: Part-time",
         "DEBT_INSECURE_W54_Yes" = "Unsecured Debt: Yes",
         "DEBT_SECURE_W54_Yes" = "Secure Debt: Yes",
         "F_E3_W54_Not employed" = "Employment: Unemployed",
         "WORRY2c_comp_W54_Yes" = "Financial Strain: Yes",
         "WORRY2c_comp_W54_No" = "Financial Strain: No",
         "F_AGECAT_W64_65+" = "Age: 65+")
```

## Helper functions for filtering data

```{r}
# Filters data to get only data from a given set of waves
# inputs: 
# - tmp: data-set to filter
# - waves: list of waves as "W*" where * is an integer wave number.
# Note: tmp must have columns called F_RESPONDED_W* where *  
responded <- function(tmp, waves) {
  message(paste0("Pre filter N=",dim(tmp)[1]))
  for (wave in waves) {
     tmp <- tmp %>% filter(!!sym(paste("F_RESPONDED",wave,sep="_")) == 1)
  }
  message(paste0("Post filter  N=",dim(tmp)[1]))
  return(tmp)
}

# Filters out missing data
# inputs: 
# - tmp: data-set to filter
# - cov: list of covariates for which to filter missing data
# - return: boolean indicating whether to return the filtered data
# - quiet: boolean indicating whether to print missing data numbers for each cov
no_missing <- function(tmp, cov,return=TRUE,quiet=FALSE) {
  #message(paste0("Pre filter N=",dim(tmp)[1]))
  for (c in cov) {
    N0 <- dim(tmp)[1]
    tmp <- tmp  %>% filter(!!sym(c) != "Refused/Missing" & 
                             !!sym(c) != "Refused" & 
                             !is.na(!!sym(c)) & 
                             !!sym(c)!="              " &
                             !!sym(c)!="                         ")
    if (!quiet) {
      message(paste("  missing",c,":",N0 - dim(tmp)[1]))
    }
  }
  if (return) {
    message(paste("Post filter",dim(tmp)[1]))
    return(tmp)
  }
}
```

## Filter to only data with the five waves
```{r}
five_waves <- W_wide %>% responded(waves=c("W54","W64","W72","W83","W114"))
```
## Impute missing and set reference levels

### Before imputation:
```{r echo=FALSE}
for (x in propensity_vars) {
  pre_imputation <- no_missing(five_waves,x,return=FALSE)
}
```

```{r }
five_waves_imputed <- five_waves %>% mutate(
  F_SEX_W64 = case_when(
    is.na(F_SEX_W64) ~ F_SEX_W54,
    TRUE ~ F_SEX_W64),
  F_AGECAT_W64 = case_when(
    is.na(F_AGECAT_W54) & !is.na(F_AGECAT_W64) ~ F_AGECAT_W64,
    is.na(F_AGECAT_W54) & !is.na(F_AGECAT_W72)~ F_AGECAT_W72,
    is.na(F_AGECAT_W54) & !is.na(F_AGECAT_W83) ~ F_AGECAT_W83,
    is.na(F_AGECAT_W54) & !is.na(F_AGECAT_W114) ~ F_AGECAT_W114,
    TRUE ~ F_AGECAT_W54),
  F_RACETHN_W64 = case_when(
    (F_RACETHN_W64=="Refused" | is.na(F_RACETHN_W64)) & (!is.na(F_RACETHN_W54) & F_RACETHN_W54!="Refused") ~ F_RACETHN_W54,
    (F_RACETHN_W64=="Refused" | is.na(F_RACETHN_W64)) & (!is.na(F_RACETHNMOD_W72) & F_RACETHNMOD_W72!="Refused") ~ F_RACETHNMOD_W72,
    (F_RACETHN_W64=="Refused" | is.na(F_RACETHN_W64)) & (!is.na(F_RACETHNMOD_W83) & F_RACETHNMOD_W83!="Refused") ~ F_RACETHNMOD_W83,
    (F_RACETHN_W64=="Refused" | is.na(F_RACETHN_W64)) & (!is.na(F_RACETHNMOD_W114) & F_RACETHNMOD_W114!="Refused") ~ F_RACETHNMOD_W114,
    TRUE ~ F_RACETHN_W64),
F_MARITALMOD_W64 = case_when(
    is.na(F_MARITALMOD_W64) &
    is.na(F_MARITALMOD_W64) &  !(is.na(F_MARITALMOD_W54)) ~ F_MARITALMOD_W54,
    TRUE ~ F_MARITALMOD_W64),
F_EDUCCAT2_W64 = case_when(
    is.na(F_EDUCCAT2_W64) & !is.na(F_EDUCCAT2_W54) ~ F_EDUCCAT2_W54,
    is.na(F_EDUCCAT2_W64) & !is.na(F_EDUCCAT2_W72) ~ F_EDUCCAT2_W72,
    is.na(F_EDUCCAT2_W64) & !is.na(F_EDUCCAT2_W83) ~ F_EDUCCAT2_W83,
    is.na(F_EDUCCAT2_W64) & !is.na(F_EDUCCAT2_W114) ~ F_EDUCCAT2_W114,
    TRUE ~ F_EDUCCAT2_W64),  
F_EDUCCAT2_W64 = case_when(
    F_EDUCCAT2_W64 == "H.S. graduate or less" ~ "Less than high school",
    F_EDUCCAT2_W64 == "College graduate/some post grad" ~ "College graduate+",
    F_EDUCCAT2_W64 == "Some college, no degree" ~ "Some college",
    F_EDUCCAT2_W64 == "Some College" ~ "Some college",
    TRUE ~ F_EDUCCAT2_W64),
F_CITIZEN_W64 = case_when(
  is.na(F_CITIZEN_W64) & !is.na(F_CITIZEN_W54) ~ F_CITIZEN_W54,
  is.na(F_CITIZEN_W64) & !is.na(F_CITIZEN_W114) ~ F_CITIZEN_W114,
  TRUE ~ F_CITIZEN_W64),
INC_TIER2_W54 =  case_when(
  is.na(INC_TIER2_W54)& !is.na(INC_TIER2_W64) ~ INC_TIER2_W64,
  is.na(INC_TIER2_W54)& !is.na(F_INC_TIER2_W83) ~ F_INC_TIER2_W83,
  is.na(INC_TIER2_W54)& !is.na(F_INC_TIER2_W114) ~ F_INC_TIER2_W114,
  TRUE ~ INC_TIER2_W54)) %>%
 mutate(INC_TIER2_W54 = relevel(INC_TIER2_W54,ref="Upper income"),
        WORRY2c_comp_W54=relevel(WORRY2c_comp_W54,ref="No"),
        DEBT_SECURE_W54=relevel(DEBT_SECURE_W54,ref="No"),
        DEBT_INSECURE_W54=relevel(DEBT_INSECURE_W54,ref="No"),
        FINANCEa_W54=relevel(FINANCEa_W54,ref="Yes"),
        F_AGECAT_W64=relevel(F_AGECAT_W64,ref="50-64"),
        F_MARITALMOD_W64=relevel(factor(F_MARITALMOD_W64),ref="Married"),
        F_EDUCCAT2_W64=relevel(factor(F_EDUCCAT2_W64),ref="Postgraduate"),
        F_CREGION_W64=relevel(F_CREGION_W64,ref="South"),
        COVID_MENTAL_W64=relevel(COVID_MENTAL_W64,ref="No"),
        F_PARENT_W54=relevel(factor(F_PARENT_W54),ref="No"))
```

### After imputation:
```{r echo=FALSE}
for (x in propensity_vars) {
  no_missing(five_waves_imputed,x,return=FALSE)
}

```

## Filter out the 65+ age category
```{r}
younger <- five_waves_imputed %>% filter(F_AGECAT_W64!="65+")
nrow(younger)
```


```{r echo=FALSE}
message(paste("Removing age greater than or equal to  65: n =",
              nrow(five_waves_imputed) - nrow(younger),
              round((nrow(five_waves_imputed) - nrow(younger)) /nrow(five_waves_imputed),3)*100, "%"))


```

## Remove those missing COVIDWORK W64 

```{r}
NA_exp64 <- younger %>% filter(
COVIDWORK_W64_both_not_na==0) %>% nrow()
```


```{r echo=FALSE}
message(paste("COVIDWORK W64 missing data: n =",
              NA_exp64,
              round(NA_exp64 / nrow(younger),3)*100, "%"))
```

## Remove those who experienced job or income loss by March 2020
```{r}
YES_exp64 <- younger %>% filter(COVIDWORK_comp_bin_W64==1) %>% nrow()
```


```{r echo=FALSE}
message(paste("COVIDWORK W64 Yes: n =",
              YES_exp64,
              round(YES_exp64/nrow(younger),3)*100, "%"))

younger_no64 <- younger %>% filter(COVIDWORK_comp_bin_W64==0)
nrow(younger_no64)
```

## Remove those who answered "not applicable not employed" august 2020 income loss 
```{r}
younger_no64_employed <- younger_no64 %>% filter(!(COVIDWORK_comp_W72 == "Not applicable (not employed)" | COVIDWORK_comp_W72 == "Refused/Missing"))
nrow(younger_no64_employed )
```


```{r echo=FALSE}
message(paste("COVIDWORK 72 Not applicable: n =",
              nrow(younger_no64) - nrow(younger_no64_employed),
              round((nrow(younger_no64) - nrow(younger_no64_employed))/nrow(younger_no64),3)*100, "%"))
```

## Remove those with missing August income loss
```{r}
tmp <- nrow(younger_no64_employed)
tmp_dat <- younger_no64_employed
younger_no64_employed <- younger_no64_employed %>% filter(!is.na(COVIDWORK_comp_bin_W72))


```


```{r echo=FALSE}
message(paste("COVIDWORK 72 missing: n =",
              tmp - nrow(younger_no64_employed),
              round((tmp - nrow(younger_no64_employed))/tmp,3)*100, "%"))

```

## Remove those missing outcome data
```{r}
younger_no64_employed_nomiss_psyc <- younger_no64_employed %>% no_missing(cov=c(distress))
```

```{r echo=FALSE}
message(paste("Psych data missing: n =",
              nrow(younger_no64_employed) - nrow(younger_no64_employed_nomiss_psyc),
              round((nrow(younger_no64_employed) - nrow(younger_no64_employed_nomiss_psyc))/tmp,3)*100, "%"))
```
## Remove those missing covariate data
```{r}
younger_no64_employed_nomiss_psyc_prop <- younger_no64_employed_nomiss_psyc %>% no_missing(propensity_vars)  %>% droplevels()
```

```{r echo=FALSE}
message(paste("propensity vars missing: n =",
              nrow(younger_no64_employed_nomiss_psyc) - nrow(younger_no64_employed_nomiss_psyc_prop ),
              round((nrow(younger_no64_employed_nomiss_psyc) - nrow(younger_no64_employed_nomiss_psyc_prop))/tmp,3)*100, "%"))


```
## Summary

```{r echo=FALSE}
message(paste("Out of .... N= ",
              tmp,
              "excluded missing n=",
              tmp-nrow(younger_no64_employed_nomiss_psyc_prop),
              round((tmp-nrow(younger_no64_employed_nomiss_psyc_prop))/tmp,3)*100, "%",
              "for a total of",
              nrow(younger_no64_employed_nomiss_psyc_prop)))

```

## Table comparing missing to non-missing

```{r}
tmp_dat <- tmp_dat %>%
  mutate(Missing_dat = case_when(
    QKEY %in% younger_no64_employed_nomiss_psyc_prop$QKEY ~ "No missing data",
    TRUE ~ "Missing some data")) %>% mutate(across(all_of(c("COVIDWORK_comp_W72",propensity_vars)),
                                                   function(x) case_when(x=="Refused/Missing" ~ NA,
                                                                         x=="Refused/Missing              "  ~ NA,
                                                                         TRUE ~ x))) %>% droplevels() 

missing_tab <- svydesign(~1, data = tmp_dat, weights = ~WEIGHT_W54_64_72_83_114) %>% 
  tbl_svysummary(by=Missing_dat,
                 digits = list(all_categorical() ~ c(0, 1)),
                 label=c(list(COVIDWORK_comp_W72="Mid-pandemic income or job loss"),propensity_vars_labels,outcome_labels),
                 include=all_of(c("COVIDWORK_comp_W72",propensity_vars,distress)),
                 statistic = list(
                   all_categorical() ~ "{n_unweighted} ({p})",
                   all_continuous() ~ "{mean} ({sd})")) %>%
  modify_header(all_stat_cols() ~ "**{level}**, n={n_unweighted} ({style_percent(p)}%)") %>%
  modify_footnote(all_stat_cols() ~ "Unweighted N (Weighted %). Weighted with longitudinal survey weights.") %>% 
  modify_caption("**eTable 2:** Demographic characteristics, pre-pandemic finances, lifetime diagnosis of a mental health condition, and psychological distress, by missing data status")
missing_tab
```

## Save analytic dataset 

```{r}
analytic <- younger_no64_employed_nomiss_psyc_prop 
write_sav(analytic, here("data","analytic.sav"))
```

# Analysis 

## Table 1

```{r}
t1 <- svydesign(~1, data = analytic, weights = ~WEIGHT_W54_64_72_83_114) %>% 
  tbl_svysummary(by=COVIDWORK_comp_W72,                                               
                 label=c(propensity_vars_labels,outcome_labels),
                 include=all_of(c(propensity_vars,distress)),
                 digits = list(all_categorical() ~ c(0, 1)),
                 statistic = list(
                   all_categorical() ~ "{n_unweighted} ({p})",
                   all_continuous() ~ "{mean} ({mean.std.error})")) %>%
  modify_header(all_stat_cols() ~ "{level}, {n_unweighted} ({style_percent(p)}%)") %>%
  modify_footnote(all_stat_cols() ~ "Unweighted N (Weighted %). Weighted with longitudinal survey weights.") %>%
  modify_spanning_header(all_stat_cols() ~ "**Mid-pandemic Income or job loss**") %>% 
  add_overall(col_label = "**Overall** {n_unweighted}")  %>% 
  modify_caption("**Table 1:** Demographic characteristics, pre-pandemic finances, lifetime diagnosis of a mental health condition, and psychological distress (March 2020) for the analytic sample")

t1
```


## Propensity scores
```{r}
f_ps <- as.formula(paste0("COVIDWORK_comp_bin_W72 ~",  paste0(propensity_vars, collapse= "+")))
f_ps
```


```{r}
w.out_glm <- weightit(f_ps, 
                      data = analytic,
                      estimand= "ATT",
                      method="ps",
                      s.weights="WEIGHT_W54_64_72_83_114")
```

### Table with numbers for use in "**eResults**: Propensity score and weight distribution"

```{r}
tibble(w=w.out_glm$weights,pss=w.out_glm$ps,exp=w.out_glm$treat) %>%
  group_by(exp) %>%
  mutate(exp=case_when(exp==0~"No income loss",
                       exp==1 ~"Yes, income loss")) %>% 
  summarize("min(weights)"=round(min(w),2),
            "max(weights)"=round(max(w),2),
            "median(weights)"=round(median(w),2),
            "min(PS)"=round(min(pss),2),
            "max(PS)"=round(max(pss),2),
            "median(PS)"=round(median(pss),2))

```

### **Figure 1**: Survey weighted covariate balance before and after propensity score weighting
```{r fig.height=6,fig.width=7, fig.caption="Pew Research Center’s American Trends Panel data. Sample: Adults 18-64 years in the U.S. who had not experienced income or job loss by March 24, 2020 (N=1392). Standardized mean differences are computed for each covariate group, before propensity score adjustment (using only survey weights) and after propensity score weighting (using both survey wights and propensity score weights), comparing the covariate balance between the group who experienced early phase pandemic income loss and those who did not experience pandemic income loss. The dashed lines at -0.1 and 0.1 indicate a cut-off for acceptable balance defined in Austin (2011)."}
love.plot(f_ps,
          data = analytic, 
          weights = w.out_glm,
          var.order = "unadjusted", binary = "std",
          abs = FALSE, 
          title="",
          shapes = c("circle filled", "circle"),
          colors=c("black","black"),
          sample.names=c("Survey Weighted","PS and Survey Weighted"),
          var.names=love_labels,
          thresholds = c(m = .1),
          line = TRUE,s.weights="WEIGHT_W54_64_72_83_114") + theme_bw() + theme(legend.position="bottom",#c(.77,.1), 
      legend.title =element_blank(),
      legend.box.margin = margin(t = -11, 0, 0, 0),
      legend.text=element_text(size=rel(0.75)))

ggsave(file.path(fig_path,"figure1.pdf"),width=7,height=6)
```


### **eFigure 2:** Distribution of propensity scores by income or job loss group

```{r fig.width=7,fig.height=5,fig.caption="The distribution of propensity scores (estimated probability of experiencing income or job loss between March 24, 2020 and August 16, 2020) is shown among the groups who did and did not experience income or job loss, in our sample of adults 18-64 years in the U.S. who had not experienced income or job loss by March 24, 2020 (N=1392). Data comes from the of Pew Research Center’s American Trends Panel data."}

tibble("exp"=w.out_glm$treat,"ps"=w.out_glm$ps) %>% 
  ggplot() + geom_density(aes(x=ps,fill=factor(exp)),colour="black",alpha=.75) +xlab("Propensity score")+ theme_bw() +
 scale_fill_brewer(name="Job or income loss",palette = "Set1",labels=c("No","Yes"))+ theme(legend.position=c(.825,.825), 
      legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid'),
      legend.box.margin = margin(t = -11, 0, 0, 0),
      legend.text=element_text(size=rel(0.75)))

  #scale_shape_manual(values=c("1"=16,"0"=1)) #+ 
  #scale_y_continuous(limits=c(0,.75)) + scale_x_discrete(labels=c("No","Yes"))

ggsave(file.path(fig_path,"efigure1.pdf"),width=7,height=4.5)
```


### **eFigure 3**: Distribution of propensity score weights among those who did not experience income or job loss 

```{r fig.width=7,fig.height=5, fig.cap=" A histogram of propensity score weights is shown for those who did not report income or job loss by August 16, 2020 (n=955). Those who did report income or job loss between March 24, 2020 and August 16, 2020 are assigned weights of one. Data comes from the of Pew Research Center’s American Trends Panel data."}
tibble("exp"=w.out_glm$treat,weight=w.out_glm$weights) %>% 
  filter(exp==0) %>% 
  ggplot() + geom_histogram(aes(x=weight),fill="darkgray",colour="black") +xlab("Propensity score weights") + ylab("Count") + theme_bw()# + scale_x_continuous(limits=c(0,2))
ggsave(file.path(fig_path,"efigure2.pdf"),width=7,height=4.5)
```

## **eTable 3**: Propensity score modela and covariate balance 

```{r}
## logistic regression model
ps_design <-svydesign(id=~QKEY,weights=~WEIGHT_W54_64_72_83_114, data=analytic)

m1 <- svyglm(as.formula(paste("COVIDWORK_comp_bin_W72 ~",                       
                      paste(propensity_vars,collapse="+"))),
             design=ps_design,
             family="binomial")

job_loss_model_table <- tbl_regression(m1,exponentiate=TRUE,label=propensity_vars_labels)

## Balance table
bal <- bal.tab(f_ps, data = analytic, 
        weights = list(glm = w.out_glm$weights),
        un=TRUE,
        binary = "std",
        disp.v.ratio = TRUE,
        s.weights="WEIGHT_W54_64_72_83_114")

bal_tibble <- tibble("variable" = rownames(bal$Balance),
                     "UnadjustedSMD"=bal$Balance$Diff.Un,
                     "AdjustedSMD"=bal$Balance$Diff.Adj) %>%
  separate(variable,into=c("variable","label"),sep="(?<=_W(\\d\\d)_)") %>%
  mutate(label = ifelse(variable==pre_exp,"",label),
         "variable" = ifelse(variable==pre_exp,variable,
                             substr(variable,1, nchar(variable)-1)),
         "UnadjustedSMD" = round(UnadjustedSMD,3),
         "AdjustedSMD" = round(AdjustedSMD,3)) %>% 
  mutate(term = paste0(
variable, label)) %>% select(-variable,-label)

# set up combined table
comb_table <- job_loss_model_table
comb_table$table_body <- left_join(job_loss_model_table$table_body,bal_tibble,by="term")

# formatting for combined table
comb_table$table_styling$header <- comb_table$table_styling$header %>%
  add_row(column="UnadjustedSMD",
          hide=FALSE,
          interpret_label="gt::md",
          align="center",
          label="Unadjusted",
          interpret_spanning_header="gt::md",
          spanning_header="**Standardized Mean Difference (SMD)**") %>% 
  add_row(column="AdjustedSMD",
          hide=FALSE,
          interpret_label="gt::md",
          align="center",
          label="Adjusted",
          interpret_spanning_header="gt::md",
          spanning_header="**Standardized Mean Difference (SMD)**") 

comb_table
```
We used a multivariable survey weighted logistic regression to model the probability of experiencing income or job loss between March 24, 2020 - August 16, 2020. Adjusted odds ratio (aOR), 95% confidence intervals (CI), and p-value are reported for each covariate.  The analytic sample consists of U.S. adults aged 18-64 who did not experience income or joss before March 24, 2020. Standardized mean difference (SMD). Unadjusted: Survey weighted only. Adjusted: Survey and propensity score weighted. A dash indicates a reference level. For two-category variables, reference level is not displayed.

## Main analysis
### **eTable 4:** Estimated association between early-pandemic income or job loss and pandemic psychological stress score
```{r}

design.main <- svydesign(ids=~QKEY, 
                         weights=w.out_glm$weights *analytic$WEIGHT_W54_64_72_83_114,
                         data=analytic)

f_glm_W64 <- as.formula(paste("MH_TRACK_int_W64 ~COVIDWORK_comp_bin_W72 +",paste(propensity_vars[propensity_vars!="MH_TRACK_int_W64"], collapse= "+")))
glm_W64 <- svyglm(f_glm_W64, design=design.main,family="quasipoisson")

f_glm_W83 <- as.formula(paste("MH_TRACK_int_W83 ~COVIDWORK_comp_bin_W72 +",paste(propensity_vars, collapse= "+")))
glm_W83 <- svyglm(f_glm_W83, design=design.main,family="quasipoisson")

f_glm_W114 <- as.formula(paste("MH_TRACK_int_W114 ~COVIDWORK_comp_bin_W72 +",paste(propensity_vars, collapse= "+")))
glm_W114 <- svyglm(f_glm_W114, design=design.main,family= "quasipoisson")


reg_tables_64 <- tbl_regression(glm_W64,include="COVIDWORK_comp_bin_W72",exponentiate = TRUE,label=c(COVIDWORK_comp_bin_W72="Income or job loss"))
reg_tables_83 <- tbl_regression(glm_W83,include="COVIDWORK_comp_bin_W72",exponentiate = TRUE,label=c(COVIDWORK_comp_bin_W72="Income or job loss"))
reg_tables_114 <- tbl_regression(glm_W114,include="COVIDWORK_comp_bin_W72",exponentiate = TRUE,label=c(COVIDWORK_comp_bin_W72="Income or job loss"))

distress_tables <- tbl_stack(list(reg_tables_64,reg_tables_83,reg_tables_114),group_header=list("Mar. 2020","Feb. 2021","Sept. 2022"))

distress_tables
```
### Confirm that the exponentiated coefficient is the same as the ratio obtained in marginal effects package
```{r}

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= glm_W64,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                 weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)


marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= glm_W83,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                 weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= glm_W114,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                  weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)

```

### Compute estimates as a difference in means
```{r}

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "differenceavg",
                                 model= glm_W64,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                  weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "differenceavg",
                                 model= glm_W83,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                  weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "differenceavg",
                                 model= glm_W114,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                  weights=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)


```


## OLS instead of quasi-poisson
```{r}
lm_W83 <- svyglm(f_glm_W83, design=design.main,family="gaussian")
lm_W114 <- svyglm(f_glm_W114, design=design.main,family= "gaussian")

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "differenceavg",
                                 model= lm_W83,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                 wts=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)

marginaleffects::avg_comparisons(type = "response",
                                 comparison = "difference",
                                 model= lm_W114,
                                 newdata=subset(analytic,COVIDWORK_comp_bin_W72==1),
                                 variables="COVIDWORK_comp_bin_W72",
                                  wts=subset(analytic,COVIDWORK_comp_bin_W72==1)$WEIGHT_W54_64_72_83_114)
```

## Figure 2
```{r fig.width=7,fig.height=5}
results_plot_table <- distress_tables$table_body %>% mutate("label"=unlist(groupname_col)) %>% select("label","estimate","conf.low","conf.high") %>% mutate("time"= case_when(
          label== "Mar. 2020"~ as.Date("2020-03-24"),
           label == "Feb. 2021" ~ as.Date("2021-02-16"),
           label== "Sept. 2022" ~ as.Date("2022-09-13"))) 

results_plot_table %>%  ggplot() + geom_point(aes(x=time,y=estimate),colour="black") +
  geom_errorbar(aes(x=time,ymin=conf.low,ymax=conf.high),width=20,colour="black") +
  geom_line(aes(x=time,y=estimate),colour="black")+ 
  geom_hline(yintercept=1,linetype="dashed",colour="black") + 
  theme_bw() +
  annotate('rect', xmin=as.Date("2020-03-24"), xmax=as.Date("2020-08-16"), ymin=.80, ymax=1.3, alpha=.3, fill='gray') +
  ylab("Estimated ratio of psychological distress scores") + scale_y_continuous(breaks=c(.8,.9,1,1.1,1.2,1.3)) +
  scale_x_date(breaks=c(as.Date("2020-03-24"),as.Date("2020-08-16"),as.Date("2021-02-16"),as.Date("2022-09-13")),label=c("Mar. 2020","Aug. 2020","Feb. 2021","Sept. 2022")) + 
  theme(legend.margin=margin(t=-20), 
        legend.text = element_text(size=rel(.75)),
        legend.position = "bottom") + xlab("")
ggsave(file.path(fig_path,"figure2.pdf"),width=7,height=5)
```

### Figure 2 with title and caption

```{r}
p <- results_plot_table %>%  ggplot() + 
  geom_point(aes(x=time,y=estimate),col="black") +
  geom_errorbar(aes(x=time,ymin=conf.low,ymax=conf.high),width=20,col="black") +
  geom_line(aes(x=time,y=estimate),col="black")+ 
  geom_hline(yintercept=1,linetype="dashed",col="black") + 
  theme_bw() +
  annotate('rect', xmin=as.Date("2020-03-24"), xmax=as.Date("2020-08-16"), ymin=.80, ymax=1.3, alpha=.3, fill='gray') +
  ylab("Estimated ratio of psychological distress scores") + scale_y_continuous(breaks=c(.8,.9,1,1.1,1.2,1.3)) +
  scale_x_date(breaks=c(as.Date("2020-03-24"),as.Date("2020-08-16"),as.Date("2021-02-16"),as.Date("2022-09-13")),label=c("Mar. 2020","Aug. 2020","Feb. 2021","Sept. 2022")) + 
  theme(legend.margin=margin(t=-20), 
        legend.text = element_text(size=rel(.75)),
        legend.position = "bottom") + xlab("") +
  labs(subtitle="Adjusted ratio of psychological distress scores (with 95% CI) for mid-pandemic income or job loss",
       caption="Data: Pew Research Center American Trends Panel. Sample: Adults 18-64 years in the U.S. who had not experienced income or job loss by March 24, 2020 (N=1392). The light gray region represents the time (March 24-August 16, 2020) during which mid-pandemic income or job loss occurred. The figure shows the exponentiated coefficients and 95% confidence intervals for covariate-adjusted, survey and propensity score weighted quasi-Poisson models.") 
p
grattantheme::wrap_labs(p,type="normal",labs_to_wrap = c("caption"))
ggsave(file.path(fig_path,"figure_wCaption_title.pdf"))
```

## E-value

### Feb. 2021
```{r}
message(results_plot_table[2,]$label)
evalues.RR(est = results_plot_table[2,]$estimate, 
           lo = results_plot_table[2,]$conf.low, 
           hi = results_plot_table[2,]$conf.high)
```
### Sept 2022

```{r}
message(results_plot_table[3,]$label)
evalues.RR(est = results_plot_table[3,]$estimate,
           lo = results_plot_table[3,]$conf.low,
           hi = results_plot_table[3,]$conf.high)
```
# Extras (not included in paper)

## Supplemental comparison between logistic regression and GBM propensity score weights 

```{r fig.height=6,fig.width=7}
f_ps

w.out_gbm <- weightit(f_ps, data = analytic,
                        estimand= "ATT",method="gbm",stop.method="ks.mean",s.weights="WEIGHT_W54_64_72_83_114")

love.plot(f_ps,
          data = analytic, 
          weights = list("Logistic Regression"=w.out_glm$weights,"Gradient Boosted Model (GBM)"=w.out_gbm$weights),
          var.order = "unadjusted", binary = "std",
          abs = FALSE, 
          stop.method = "ks.mean",
          title="",
          var.names=love_labels,
          thresholds = c(m = .1),
          line = TRUE,s.weights="WEIGHT_W54_64_72_83_114")  + theme(legend.position=c(.8,.2), legend.title =element_text(size=rel(0.8)),legend.text=element_text(size=rel(0.75)), legend.background = element_rect(linetype = 1, size = 0.5, colour = 1))

```

## Extra weight tables / plots 
```{r fig.width=7,fig.height=5}
weight_table <- cbind("Logistic PS" = w.out_glm$weights,
                      "GBM PS"=w.out_gbm$weights,
                      "Survey" =analytic$WEIGHT_W54_64_72_83_114,
                      "Logistic PS * Survey"=analytic$WEIGHT_W54_64_72_83_114 * w.out_glm$weights,
                      "GBM PS * Survey"=analytic$WEIGHT_W54_64_72_83_114 * w.out_gbm$weights) %>% 
  as_tibble() %>% 
  mutate("Group"=analytic$group) %>%
  pivot_longer(cols=c("Logistic PS",
                      "GBM PS",
                      "Survey",
                      "Logistic PS * Survey","GBM PS * Survey"),
               names_to = "Type",
               values_to="Weight") %>% 
  mutate("Type"=factor(Type,levels=c("Logistic PS","GBM PS","Survey","Logistic PS * Survey","GBM PS * Survey"))) 


weight_table %>% ggplot() + 
  geom_histogram(aes(x=Weight,fill=Group)) + 
  facet_wrap(.~Type,ncol=3) +
  ylab("N") + theme_bw() + theme(legend.position=c(.85,.35))

```

## plot of avg psychological distress (survey weighted, not ps weighted) over time with SE
```{r fig.width=7,fig.height=5}
prev <- svydesign(~1, data = analytic, weights = ~WEIGHT_W54_64_72_83_114) %>% 
  tbl_svysummary(by=group,
                 label=propensity_vars_labels,
                 include=all_of(c(distress)),
                 statistic = list(all_continuous() ~ "{mean} ({mean.std.error})"))

prev$table_body %>% 
  select("label","stat_1","stat_2") %>%
  pivot_longer(cols = c("stat_1","stat_2"), names_to = "group",names_prefix="(stat_)") %>% 
  separate(value, c("mean", "SE"), sep = "\\(") %>% mutate(SE= str_remove(SE, "\\)")) %>% 
  mutate("group"=case_when(group=="1"~"Mid-pandemic income loss",group=="2"~"No income loss"), 
         "WAVE" = case_when(
           endsWith(label, "W64") ~ "W64", 
           endsWith(label, "W83")~ "W83",
           endsWith(label, "W114")~ "W114"),
         "time"= case_when(
           WAVE == "W64" ~ as.Date("2020-03-24"),
           WAVE == "W83" ~ as.Date("2021-02-16"),
           WAVE== "W114" ~ as.Date("2022-09-13"))) %>% 
  mutate("mean"=as.numeric(mean),"SE"=as.numeric(SE)) %>% 
  ggplot() + geom_point(aes(x=time,y=as.numeric(mean))) +
    geom_errorbar(aes(x=time,ymin=mean-SE,ymax=mean+SE,linetype=group),width=20) +
    geom_line(aes(x=time,y=as.numeric(mean),linetype=group,group=group))+ 
    theme_bw() +
    annotate('rect', xmin=as.Date("2020-03-24"), 
             xmax=as.Date("2020-08-16"), ymin=4, ymax=6.5, alpha=.3, fill='gray') + 
    ylab("Psychological distress score, mean (SE)") +
    labs(title="Survey weighted (not PS weighted",linetype=NULL) + scale_y_continuous(breaks=c(4,4.5,5,5.5,6)) +
    scale_x_date(breaks=c(as.Date("2020-03-24"),as.Date("2020-08-16"),as.Date("2021-02-16"),as.Date("2022-09-13")),
                 label=c("Mar. 2020","Aug. 2020","Feb. 2021","Sept. 2022")) + 
    theme(legend.margin=margin(t=-20), 
          legend.text = element_text(size=rel(.75)),
          legend.position = "bottom") + xlab("")
```
## Plot of avg psychological distress (survey weighted AND PS-weighted) over time, with SE
```{r fig.width=7,fig.height=5}
prev_ps <- design.main %>% 
  tbl_svysummary(by=group,
                 label=propensity_vars_labels,
                 include=all_of(c(distress)),
                 statistic = list(all_continuous() ~ "{mean} ({mean.std.error})"))

prev_ps$table_body %>% 
  select("label","stat_1","stat_2") %>%
  pivot_longer(cols = c("stat_1","stat_2"), names_to = "group",names_prefix="(stat_)") %>% 
  separate(value, c("mean", "SE"), sep = "\\(") %>% mutate(SE= str_remove(SE, "\\)")) %>% 
  mutate("group"=case_when(group=="1"~"Mid-pandemic income loss",group=="2"~"No income loss"), 
         "WAVE" = case_when(
           endsWith(label, "W64") ~ "W64", 
           endsWith(label, "W83")~ "W83",
           endsWith(label, "W114")~ "W114"),
         "time"= case_when(
           WAVE == "W64" ~ as.Date("2020-03-24"),
           WAVE == "W83" ~ as.Date("2021-02-16"),
           WAVE== "W114" ~ as.Date("2022-09-13"))) %>% 
  mutate("mean"=as.numeric(mean),"SE"=as.numeric(SE)) %>% 
  ggplot() + geom_point(aes(x=time,y=as.numeric(mean))) +
    geom_errorbar(aes(x=time,ymin=mean-SE,ymax=mean+SE,linetype=group),width=20) +
    geom_line(aes(x=time,y=as.numeric(mean),linetype=group,group=group))+ 
    theme_bw() +
    annotate('rect', xmin=as.Date("2020-03-24"), 
             xmax=as.Date("2020-08-16"), ymin=4, ymax=6.5, alpha=.3, fill='gray') + 
    ylab("Psychological distress score, mean (SE)") +
    labs(title="Survey and PS weighted",linetype=NULL) + scale_y_continuous(breaks=c(4,4.5,5,5.5,6)) +
    scale_x_date(breaks=c(as.Date("2020-03-24"),as.Date("2020-08-16"),as.Date("2021-02-16"),as.Date("2022-09-13")),
                 label=c("Mar. 2020","Aug. 2020","Feb. 2021","Sept. 2022")) + 
    theme(legend.margin=margin(t=-20), 
          legend.text = element_text(size=rel(.75)),
          legend.position = "bottom") + xlab("")
```

```{r}


db_test <- function(s) {
  X <- runif(n = 10000, 0, 2)
  probs <- 1 / (1 + exp(-X))
  Z <- sapply(probs, function(p) rbinom(1, 1, p))
  lambda <- X + Z + X*Z
  Y <- sapply(lambda, function(m) rpois(1, exp(m)))
  data <- cbind(id = 1:10000, X, Z, Y) %>% as_tibble()
  
  w.out_incorrect <- weightit(Z ~ 1, data = data, estimand = "ATT", method = "ps")
  design_incorrect <- svydesign(id = ~id, weights = ~w.out_incorrect$weights, data = data)
  
  w.out_correct <- weightit(Z ~ X, data = data, estimand = "ATT", method = "ps")
  design_correct <- svydesign(id = ~id, weights = ~w.out_correct$weights, data = data)
  
  correct_outcome_wrong_ps <- svyglm(Y ~ X * Z, design = design_incorrect, family = "poisson")
  wrong_outcome_correct_ps <- svyglm(Y ~ Z + X, design = design_correct, family = "poisson")
  correct_outcome_correct_ps <- svyglm(Y ~ X  * Z, design = design_correct, family = "poisson")
  wrong_outcome_wrong_ps <- svyglm(Y ~ Z + X, design = design_incorrect, family = "poisson")
  
  result <- c("CW"=marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= correct_outcome_wrong_ps ,
                                 newdata=subset(data,Z==1),
                                 variables="Z")$estimate,
  "WC"=marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= wrong_outcome_correct_ps,
                                 newdata=subset(data,Z==1),
                                 variables="Z")$estimate,
  "CC"=marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= correct_outcome_correct_ps,
                                 newdata=subset(data,Z==1),
                                 variables="Z")$estimate,
  "WW"=marginaleffects::avg_comparisons(type = "response",
                                 comparison = "lnratioavg",
                                 transform = "exp",
                                 model= wrong_outcome_wrong_ps ,
                                 newdata=subset(data,Z==1),
                                 variables="Z")$estimate)
  
  return(result)
}
tmp <- sapply(1:500, function(i) db_test(i))
tmp %>% rowMeans()
```

